Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-20 paper/ijcai/paper.tex
fixes in captions
equation within the text

		\caption{FAULT$\_$OF$\_$OMISSION distribution in the \dfj{} dataset}
		\label{fig:foos}
\end{figure}

@@

To evaluate the effectiveness of \comb{}, following related work, we compared its
performance with \sfl{} for each fault from the dataset, for $k\in\{5,10\}$, 
where $k$ is the number of classes comprising the highest faulty statements. These 
classes are obtained directly from the ranking which is calculated through \sfl{}. 
For each fault, spectra is updated and the fault ranking is re-calculated but only 
considering the $k$ highest faulty classes. We refer to these variations as SFL$^{k}$. 
After slicing each class of the top $k$ of the highest faulty classes for each fault, 
the initial spectra is updated based on the slicer output and the fault ranking is 
re-calculated. We refer to these variations as \combpar{k}. We
compared \combpar{5} and \combpar{10} against \sfl{}$^{5}$ and \sfl{}$^{10}$ using the
following metric:

\begin{equation}
    \Delta{}C = C(\textrm{SFL$^{k}$}) - C(\textrm{\combpar{k}})
\end{equation}

\noindent
where $C$ is the cost of diagnosis. $C$ is the mean ranking of all buggy statements.
$\Delta C >0$ means that the position of the faulty statement has decreased
in the ranking after applying the \combpar{k} approach. Hence, reducing the cost of
locating the bug. $\Delta C <0$ means that the 
faulty statement may be removed by \combpar{k}. $\Delta C=0$ means that the faulty statement 
remained in the same position.  We also assume a perfect bug understanding, i.e., if the developer
sees the bug in the ranking, he can say it is the faulty one.

@@

		\bottomrule
	\end{tabular}
	\caption {\ds{} reduction performance when considering $k=5$ and $k=10$}
	\label{tab:red}
\end{table}
\normalsize

>>>>

		\caption{Faults of omissions' distribution}
		\label{fig:foos}
\end{figure}

@@

To evaluate the effectiveness of \comb{}, following related work, we compared its
performance with \sfl{} for each fault from the dataset, for $k\in\{5,10\}$,
where $k$ is the number of classes comprising the highest faulty statements. These
classes are obtained directly from the ranking which is calculated through \sfl{}.
For each fault, spectra is updated and the fault ranking is re-calculated but only
considering the $k$ highest faulty classes. We refer to these variations as SFL$^{k}$.
After slicing each class of the top $k$ of the highest faulty classes for each fault,
the initial spectra is updated based on the slicer output and the fault ranking is
re-calculated. We refer to these variations as \combpar{k}. We
compared \combpar{5} and \combpar{10} against \sfl{}$^{5}$ and \sfl{}$^{10}$ using
the commonly used metric $\Delta{}C = C(\textrm{SFL$^{k}$}) - C(\textrm{\combpar{k}})$,
where $C$ is the cost of diagnosis. $C$ is the mean ranking of all buggy statements.
$\Delta C >0$ means that the position of the faulty statement has decreased
in the ranking after applying the \combpar{k} approach. Hence, reducing the cost of
locating the bug. $\Delta C <0$ means that the
faulty statement may be removed by \combpar{k}. $\Delta C=0$ means that the faulty statement
remained in the same position.  We also assume a perfect bug understanding, i.e., if the developer
sees the bug in the ranking, he can say it is the faulty one.

@@

		\bottomrule
	\end{tabular}
	\caption {\ds{} reduction for $k=5$ and $k=10$}
	\label{tab:red}
\end{table}
\normalsize
